Domain-Driven, Generative Data Model for BigPetStore

### 2014-07-19 bdcloud_paper/latex/paper.tex
Small edits to intro

\section{Introduction}
Big data applications process large, continuously-changing data sets with the general goal of information and knowledge extraction.  New tools such as Hive, Pig and Crunch \textcolor{red}{reference} based around big data frameworks such as Hadoop, Storm, and Spark \textcolor{red}{reference} are being released every day. Development, testing and benchmarking of big data software, algorithms, and infrastructure pose unique challenges.  Though software and algorithms will be deployed to large clusters for benchmarking and production usage, engineers develop and test these tools on desktops due to the speed and ease of development and debugging on a local machine and limited access to large clusters due to the high costs of purchasing, provisioning, and maintaining such clusters.  Software and algorithms are being developed at incredible speed with new releases everyday. The high speed of development driven by the need to be the first to market in a competitive field often results in buggy software.  There is great need for consistent and rigorous testing and benchmarking frameworks to aid in the identification of bugs while maintaining the high-speed of development.  Access to high-quality, semantically-rich data sets and complex, realistic analytics workflow examples that can scale from local development environments to large clusters are key to increasing access to and development of consistent and rigorour testing and benchmarking frameworks.

@@

More advanced approaches such as Oligas \cite{Alexandrov2013} and SMOTE \cite{Chawla2002} attempt to generate or extend real data sets with synthetic data sets that satisfy characteristics learned from a real reference data sets. \textcolor{red}{privacy, accuracy without details of underlying process, SMOTE - feature space} Oligos appears promising but will need to overcome several difficult challenges in automatically characterizing complex reference data to determine relevant constraints and learn accurate models.

Until such methods have reached maturity, the development of customized, domain-driven models is best suited for generating for satisfying the needs of big data software and algorithms development. For example, the Information Discovery and Analysis System (IDAS) Data Set Generator (IDSG) \cite{Jeske2005,Lin2006} was developed for the Department of Homeland Security to develop synthetic data for effectiveness of IDASs designed to identify potential terrorism threat scenarios.

. The lack of frameworks for generating semantically-rich data at arbitrary scale denies developers access to consistent data sets that can be used across a range of environments \textcolor{red}{Huppler, Pavlo}.  \textcolor{red}{standard benchmarks}

@@

In this work, we present a new domain-driven model and simulation for generating arbitrarily large, complex data for testing and benchmarking of algorithms, software, and infrastructure in the big data space. Compared with BigPetStore's previous data generator, our model and implementation can generate data which contains geospatial, temporal, and quantitative features, similar to the type of data which businesses and organizations might typically encounter. Combining the features of the TeraGen (scalability) \textcolor{red}{reference} and MovieLens (semantically rich) \textcolor{red}{reference} input data sets commonly used for big data benchmarking, we present a scalable synthetic data set generation implementation which can be used to benchmark lower level tasks (such as sorting) as well as higher level tasks (such as clustering, recommending, and search indexing) at arbitrary scale.  To validate this approach, we apply it as a drop in replacement for the current version of BigPetStore which has already been utilized to test several Hadoop deployments at terabyte scale, and is actively being adopted by a variety of companies in the software industry, and confirm that it generates data with desirable properties (global patterns and region specific transactions).

>>>>

\section{Introduction}
Big data applications process large, continuously-changing data sets with the general goal of information and knowledge extraction.  New tools such as Hive, Pig and Crunch \textcolor{red}{reference} based around big data frameworks such as Hadoop, Storm, and Spark \textcolor{red}{reference} are being released every day. Development, testing and benchmarking of big data software, algorithms, and infrastructure pose unique challenges.  Though software and algorithms will be deployed to large clusters for benchmarking and production usage, engineers develop and test these tools on desktops due to the speed and ease of development and debugging on a local machine and limited access to large clusters due to the high costs of purchasing, provisioning, and maintaining such clusters.  Software and algorithms are being developed at incredible speed with new releases everyday. The high speed of development driven by the need to be the first to market in a competitive field often results in buggy software.  There is great need for consistent and rigorous testing and benchmarking frameworks to aid in the identification of bugs while maintaining the high-speed of development.  Access to high-quality, semantically-rich data sets and complex, realistic analytics workflow examples that can scale from local development environments to large clusters are key to increasing access to and development of consistent and rigorous testing and benchmarking frameworks.

@@

More advanced approaches such as Oligas \cite{Alexandrov2013} and SMOTE \cite{Chawla2002} attempt to generate or extend real data sets with synthetic data sets that satisfy characteristics learned from a real reference data sets. \textcolor{red}{privacy, accuracy without details of underlying process, SMOTE - feature space} Oligos appears promising but will need to overcome several difficult challenges in automatically characterizing complex reference data to determine relevant constraints and learn accurate models that capture the effect of latent variables.

Until such methods have reached maturity, the development of customized, domain-driven models is best suited for satisfying the needs of big data software and algorithms development. For example, the Information Discovery and Analysis System (IDAS) Data Set Generator (IDSG) \cite{Jeske2005,Lin2006} was developed for the Department of Homeland Security to develop synthetic data for effectiveness of IDASs designed to identify potential terrorism threat scenarios.

\textcolor{red}{Huppler, Pavlo}.  \textcolor{red}{standard benchmarks}

@@

In this work, we present a new domain-driven model and simulation for generating arbitrarily large, complex data for testing and benchmarking of algorithms, software, and infrastructure in the big data space. Compared with BigPetStore's previous data generator, our model and implementation can generate data which contains geospatial, temporal, and quantitative features, similar to the type of data which businesses and organizations might typically encounter.  Combining the features of the TeraGen (scalability) \textcolor{red}{reference} and MovieLens (semantically rich) \textcolor{red}{reference} input data sets commonly used for big data benchmarking, we present a scalable synthetic data set generation implementation which can be used to benchmark lower level tasks (such as sorting) as well as higher level tasks (such as clustering, recommending, and search indexing) at arbitrary scale.  To validate this approach, we perform an example analysis designed to guide a fictional advertising campaign (a typical business use case) to demonstrate that the model generates data with desirable properties (global patterns and region specific transactions).  We have made the model's implementation available as open source software.
